Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-14 paper/evaluation.tex
First take on evaluation done.

\textbf{Interactive proofreading.} A comparison of interactive proofreading tools by Haehn~\etal~ concludes that novices perform best when using Dojo~\cite{haehn_dojo_2014}. We use the publicly available findings of their user study as a baseline comparison. More specifically, we use the data of the Dojo user with the reported best performance.

\textbf{Computer-aided proofreading.} We compare against focused proofreading by Plaza~\cite{focused_proofreading}. Focused proofreading performs graph analysis on output from NeuroProof \cite{neuroproof2013}. For training, we therefore replace GALA in our automatic segmentation pipeline with NeuroProof but use exactly the same input data including membrane probabilities. We obtained the best possible parameters for NeuroProof by consulting the developers and report them in table \ref{tab:parameters}.

@@

\textbf{Selection oracle evaluation.} We use the selection oracle as described in section~\ref{sec:errorcorrection} for the decision whether to accept or reject a correction. The purpose of this experiment is to investigate how many corrections are required to reach the best possible outcome. This is a direct comparison of the guided proofreading and focused proofreading classifiers but can only be performed if ground truth data is available. We perform this experiment on all datasets listed above.
\\~\\
\textbf{Automatic method evaluation.} For this experiment we accept all suggested corrections if the rankings are above a configured threshold $p_t=.95$ (Sec.~\ref{sec:errorcorrection}. We observed this value as stable in previous experiments with the guided proofreading classifiers (see supplementary material). We compare against the focused proofreading classifier and perform this experiment on all reported datasets.

\textbf{Forced choice user experiment.} We conduct a quantitative user study to evaluate the forced choice setting as described in section~\ref{sec:errorcorrection}. In particular, we evaluate how participants perform while correcting an automatic segmentation using the guided proofreading and focused proofreading tools. We designed a between-subjects experiment and asked the participants to proofread the AC4 subvolume in a fixed time frame of 30 minutes. 
Because we wanted to first study how completely inexperienced users perform, we recruited participants with no experience in electron microscopy data or proofreading of such through flyers, mailing lists, and personal interaction. Based on sample size calculation theory, we estimated the study sample size as ten users per proofreading tool including four potential dropouts \cite{samplesize1, samplesize2}. Nevertheless, all twenty participants completed the study ($N=20$, 10 female; 19-65 years old, $M$=30). To enable comparison against the interactive proofreading study by~Haehn~\etal~, we use the same dataset and the same time limit. 
Second, we wanted to study expert performance using guided proofreading and focused proofreading.

%\textbf{Training.}

>>>>

\textbf{Interactive proofreading.} A comparison of interactive proofreading tools by Haehn~\etal~ concludes that novices perform best when using Dojo~\cite{haehn_dojo_2014}. We use the publicly available findings of their user study as a baseline comparison. More specifically, we use the data of the Dojo user with the reported best performance.
\\~\\
\textbf{Computer-aided proofreading.} We compare against focused proofreading by Plaza~\cite{focused_proofreading}. Focused proofreading performs graph analysis on output from NeuroProof \cite{neuroproof2013}. For training, we therefore replace GALA in our automatic segmentation pipeline with NeuroProof but use exactly the same input data including membrane probabilities. We obtained the best possible parameters for NeuroProof by consulting the developers and report them in table \ref{tab:parameters}. Rather than using Raveler as the frontend, we use our own interface (Figure \ref{fig:ui}). This way, the comparison is based on the classifier rather than on user interface.

@@

\textbf{Selection oracle evaluation.} We use the selection oracle as described in section~\ref{sec:errorcorrection} for the decision whether to accept or reject a correction. The purpose of this experiment is to investigate how many corrections are required to reach the best possible outcome. This is a direct comparison of the guided proofreading and focused proofreading classifiers but can only be performed if ground truth data is available. We perform this experiment on all datasets listed above.
\\~\\
\textbf{Automatic method evaluation.} For this experiment we accept all suggested corrections if the rankings are above a configured threshold $p_t=.95$ (Sec.~\ref{sec:errorcorrection}. We observed this value as stable in previous experiments with the guided proofreading classifiers (see supplementary material). We compare against the focused proofreading classifier and perform this experiment on all reported datasets.
\\~\\
\textbf{Forced choice user experiment.} We conduct a quantitative user study to evaluate the forced choice setting as described in section~\ref{sec:errorcorrection}. In particular, we evaluate how participants perform while correcting an automatic segmentation using the guided proofreading and focused proofreading tools. We designed a single factor between-subject experiment with the factor \textit{proofreading classifier} and asked participants to proofread the AC4 subvolume in a fixed time frame of 30 minutes. To enable comparison against the interactive proofreading study by~Haehn~\etal~, we use the exact same study conditions such as dataset and time limit. The experiment was performed on the same machine with standard, off-the-shelf hardware. All participants received monetary compensation for their time.
\begin{itemize}
\item \textbf{Novice Performance.} First we wanted to study how completely inexperienced users perform. We recruited participants with no experience in electron microscopy data or proofreading of such through flyers, mailing lists, and personal interaction. Based on sample size calculation theory, we estimated the study sample size as ten users per proofreading tool including four potential dropouts \cite{samplesize1, samplesize2}. Nevertheless, all twenty participants completed the study ($N=20$, 10 female; 19-65 years old, $M$=30). Each study session started off with the participants signing the consent form and with a five minute standardized explanation of the task. The participants then were asked to do a 3 minute proofreading task on separate but representative data using focused proofreading. The participants were allowed to ask questions during this time. The classifier did not matter in this case since the user interface was the same. The experimenter then loaded the AC4 subvolume with initial pre-computed classifications by either guided proofreading or focused proofreading depending on assignment. After 30 minutes, the participants completed the raw NASA-TLX standard questions for task evaluation \cite{NASATLX}.
\item \textbf{Expert Performance.} We recruited 4 domain experts to evaluate performance of guided proofreading and focused proofreading. We obtained study consent and randomly assigned 2 experts to proofread using each classifier. The experts also did the 3 minute test run on different data prior to proofreading for 30 minutes. After the task ended, the experts were asked to complete the raw NASA-TLX questionnaire as well.
\end{itemize}

\textbf{Evaluation metric.} For each experiment, we measure the similarity between proofread segmentations and the manual ground truth labelings using \textit{variation of information} (VI). VI is a measure of the distance between two clusterings, closely related to mutual information, but lower being better. We calculate VI and treat it as a continuous variable during analysis.
